Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-22 main.tex
intro edited

\item We implement a runtime system able to provide some feedback to the scheduler
when task requirements (in terms of execution time and memory) differ from the initial predictions, 
and we recompute a schedule, based on the reported deviations.

\item We perform extensive simulations, first in the static case by comparing the schedules produced 
by these heuristics with the classical HEFT as baseline, which however does not take memory sizes into account; 
while HEFT returns invalid schedules that exceed the processor memories and cannot execute correctly,
the new heuristics are able to successfully schedule large workflows, with reasonable makespans.

\item In the dynamic setting, we use a runtime system that allows us to simulate workflow executions,
introducing deviations in running times and memory requirements of tasks that are communicated
back to the scheduler; the scheduler can then recompute a schedule. Without these recomputations,
most schedules become invalid after deviations, since the memory constraint is exceeded 
for most workflows, hence demonstrating the necessity of a dynamic adjustment of the schedule.

@@

We first review related work in Section~\ref{sec:related-work}. Then, we formalize the model in Section~\ref{sec:model}
and the algorithms in Section~\ref{sec:heuristics}. The adaptation of the heuristics in a dynamic setting is discussed in Section~\ref{sec:dyn}, and experiment results are presented in Section~\ref{sec:expe}. Finally, we conclude
and provide future working directions in Section~\ref{sec:conc}.

>>>>

\item We implement a runtime system able to provide some feedback to the scheduler
when task requirements (in terms of execution time and/or memory) differ from the initial predictions, 
and we recompute a schedule, based on the reported deviations.

\item We perform extensive simulations, first in the static case by comparing the schedules produced 
by these heuristics with the classical HEFT as baseline (the latter does not take memory sizes into account); 
while HEFT returns invalid schedules that exceed the processor memories and cannot execute correctly,
the new heuristics are able to successfully schedule large workflows and do so with reasonable makespans.

\item In the dynamic setting, we use a runtime system that allows us to simulate workflow executions.
The runtime system introduces deviations in running times and task memory requirements and communicates
them to the scheduler; the scheduler can then recompute a schedule. Without these recomputations,
most schedules become invalid after deviations, since the memory constraint is exceeded 
for most workflows, which demonstrates the necessity of a dynamic adjustment of the schedule.

@@

We first review related work in Section~\ref{sec:related-work}. Then, we formalize the model in Section~\ref{sec:model}
and present our algorithms in Section~\ref{sec:heuristics}. The adaptation of the heuristics in a dynamic setting is discussed in Section~\ref{sec:dyn}, and the results of our experiments are presented in Section~\ref{sec:expe}. Finally, we conclude
and provide future working directions in Section~\ref{sec:conc}.
